On the presentation of orthogonal groups over polynomial rings

### 2019-05-03 dl-paper.tex
Added Corollary 3

The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
 it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $g(0)$ lies in the subgroup generated by
 elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
 and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
\[ z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\beta+\alpha} (N_{\beta, \alpha}\cdot af)     \cdot z_{\beta}(Xf, \xi). \]
Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
Computing the conjugates of these generators using~\cref{Zrels} we obtain that
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \\
z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \end{align}
The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.

Let us verify the assertion for the generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
\begin{multline} \nonumber z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.

@@

>>>>

The above lemma allows us to give the following alternative characterization for the subgroup $P_\alpha(*)$:
 it consists precisely of those elements $g \in \St(\Phi, A[X], M[X])$ for which $ev_{X=0}^*(g)$ lies in the subgroup generated by
 elements $x_{\beta}(m),\ \beta \in Z_+(\alpha)$ and $z_{\gamma}(m, \zeta),\ \gamma \in Z_0(\alpha),$ where $m \in M$, $\zeta \in A$ 
 and $Z_+(\alpha)$, $Z_0(\alpha)$ are as in~\cite[Proposition~5.7]{St71}.

@@

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible for the generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- afg) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right hand side is a product of generators of type 2, 2, 1. 
Now consider the case $\alpha - \beta \in \Phi$, which is possible for the generators of type 1 and 2.
Computing the conjugates of these generators using~\cref{Zrels} we obtain that
\begin{align} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = &  x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \\
z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = & x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi). \nonumber \end{align}
The expressions in the right-hand side are products of generators of type 2, 2, 1 and 2, 1, 2.

Let us verify the assertion for the generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} of~\cref{Zrels} we obtain that
\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 1, 1, 1, 2, 2.

@@

\begin{corollary} Suppose $g$ is an element of $P_\alpha(0) \cap K(A[X], M[X])$. Then $ev^*_{X=0}(S_\alpha(a, g))$ lies in the subgroup $U(Z_+(\alpha), M)$. \end{corollary}
\begin{proof}
 By~\cref{Kgen-strong} and~\cref{P0_normal} $g$ can be expressed as a product of elements 
 $z_\beta(Xf, \xi)$, $\beta\in\Phi\setminus\{\pm \alpha\}$, $c_\gamma(f, X\xi)$ for some $\gamma$ orthogonal to $\alpha$, $x_{-\alpha}(X^2f)$, $x_{\alpha}(f)$.

 It remains to notice that in~\eqref{eq:Zconj1}--\eqref{eq:Zconj3} after evaluating at $X=0$ the only terms that remain 
  are those of the form $x_\beta(m)$ for some $\beta \in Z_+(\alpha)$.
\end{proof}
